An equivalence of compositional frameworks

### 2018-11-13 EquivCompFrameworks_20180911kc.tex
small

\begin{comment}
\begin{center}   
 % {\bf Structured cospans \\}   
  \vspace{0.3cm}
  {\em John\ C.\ Baez \\}
  \vspace{0.3cm}
  {\small
 Department of Mathematics \\
    University of California \\
  Riverside CA, USA 92521 \\ and \\
 Centre for Quantum Technologies  \\
  National University of Singapore \\
    Singapore 117543  \\    } 
 \vspace{0.4cm}
{\em Kenny Courser \\}
\vspace{0.3cm}
   {\small
  Department of Mathematics \\
  University of California \\
  Riverside CA, USA 92521 \\}
  \vspace{0.4cm}   
{\em Christina Vasilakopoulou \\}
\vspace{0.3cm}
   {\small
  Department of Mathematics \\
  University of California \\
  Riverside CA, USA 92521 \\}
  \vspace{0.3cm}   
  {\small email: baez@math.ucr.edu, courser@math.ucr.edu, vasilak@ucr.edu\\} 
  \vspace{0.3cm}   
  {\small \today}
  \vspace{0.3cm}   
\end{center}   
\end{comment}

@@

\section*{Various issues-in-progress}
{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
\begin{itemize}
\item Fix notation for structured and decorated cospans.
\end{itemize}

>>>>

@@

\section*{Various issues-in-progress}
{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
\begin{itemize}
\item Fix notation for structured and decorated cospans.
\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
and both should be presented early.}
\end{itemize}
